Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-10-06 STAT-paper-template/APA/fertile.tex
modifications to address comments

However, while the necessity of reproducibility is clear, there are significant behavioral and technical challenges that impede its widespread implementation and no clear consensus on standards of what constitutes reproducibility in published research (\cite{peng2009bio}). Not only are the components of reproducible research up for discussion (e.g., need the software be open source?), but the corresponding recommendations for ensuring reproducibility also vary (e.g., should raw and processed data files be in separate directories?).
Existing attempts to address reproducibility in data science are often either too generalized---resulting in shallow and vague recommendations that are challenging to implement---or too specific---approaching one aspect of reproducibility well but doing so in a highly technical way that fails to capture the bigger picture and creates challenges for inexperienced users.

In order to address these challenges, we present \pkg{fertile}, a low barrier-to-entry package focusing on common reproducibility mistakes programmers make while conducting data science research in R.

@@

The \func{proj\_check} function runs fifteen different reproducibility tests, noting which ones passed, which ones failed, the reason for failure, a recommended solution, and a guide to where to look for help. These tests include: looking for a clear build chain, checking to make sure the root level of the project is clear of clutter, confirming that there are no files present that are not being directly used by or created by the code, and looking for uses of randomness that do not have a call to \func{set.seed} present. A full list is provided below:

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{list_checks}\hlstd{()}
\end{alltt}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- The available checks in `fertile` are as follows: ------------------------ fertile 0.0.0.9027 --}}\begin{verbatim}
##  [1] "has_tidy_media"          "has_tidy_images"        
##  [3] "has_tidy_code"           "has_tidy_raw_data"      
##  [5] "has_tidy_data"           "has_tidy_scripts"       
##  [7] "has_readme"              "has_no_lint"            
##  [9] "has_proj_root"           "has_no_nested_proj_root"
## [11] "has_only_used_files"     "has_clear_build_chain"  
## [13] "has_no_absolute_paths"   "has_only_portable_paths"
## [15] "has_no_randomness"
\end{verbatim}
\end{kframe}
\end{knitrout}

Subsets of the fifteen tests can be invoked using the \pkg{tidyselect} helper functions (\cite{R-tidyselect}) in combination with the more limited \func{proj\_check\_some} function.

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Compiling... ------------------------------------------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... --------------------------------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Running reproducibility checks ------------------------------------------- fertile 0.0.0.9027 --}}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Summary of fertile checks ------------------------------------------------ fertile 0.0.0.9027 --}}\end{kframe}
\begin{kframe}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Analysis of reproducibility for project\_miceps --------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Packages referenced in source code ------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## # A tibble: 9 x 3
##   package       N used_in                    
##   <chr>     <int> <chr>                      
## 1 broom         1 project_miceps/analysis.Rmd
## 2 dplyr         1 project_miceps/analysis.Rmd
## 3 ggplot2       1 project_miceps/analysis.Rmd
## 4 purrr         1 project_miceps/analysis.Rmd
## 5 readr         1 project_miceps/analysis.Rmd
## 6 rmarkdown     1 project_miceps/analysis.Rmd
## 7 skimr         1 project_miceps/analysis.Rmd
## 8 stargazer     1 project_miceps/analysis.Rmd
## 9 tidyr         1 project_miceps/analysis.Rmd
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Files present in directory --------------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
##                      file   ext    size
## 1 Estrogen_Receptors.docx  docx  10.97K
## 2      citrate_v_time.png   png 188.08K
## 3     proteins_v_time.png   png 378.45K
## 4   Blot_data_updated.csv   csv  14.43K
## 5      CS_data_redone.csv   csv   7.39K
## 6                mice.csv   csv  14.33K
## 7               README.md    md      39
## 8            miceps.Rproj Rproj     204
## 9            analysis.Rmd   Rmd   4.94K
##                                                                      mime
## 1 application/vnd.openxmlformats-officedocument.wordprocessingml.document
## 2                                                               image/png
## 3                                                               image/png
## 4                                                                text/csv
## 5                                                                text/csv
## 6                                                                text/csv
## 7                                                           text/markdown
## 8                                                            text/rstudio
## 9                                                         text/x-markdown
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Suggestions for moving files ------------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
##                  path_rel    dir_rel
## 1   Blot_data_updated.csv   data-raw
## 2      CS_data_redone.csv   data-raw
## 3 Estrogen_Receptors.docx inst/other
## 4            analysis.Rmd  vignettes
## 5      citrate_v_time.png inst/image
## 6                mice.csv   data-raw
## 7     proteins_v_time.png inst/image
##                                                                                                cmd
## 1     file_move('project_miceps/Blot_data_updated.csv', fs::dir_create('project_miceps/data-raw'))
## 2        file_move('project_miceps/CS_data_redone.csv', fs::dir_create('project_miceps/data-raw'))
## 3 file_move('project_miceps/Estrogen_Receptors.docx', fs::dir_create('project_miceps/inst/other'))
## 4             file_move('project_miceps/analysis.Rmd', fs::dir_create('project_miceps/vignettes'))
## 5      file_move('project_miceps/citrate_v_time.png', fs::dir_create('project_miceps/inst/image'))
## 6                  file_move('project_miceps/mice.csv', fs::dir_create('project_miceps/data-raw'))
## 7     file_move('project_miceps/proteins_v_time.png', fs::dir_create('project_miceps/inst/image'))
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Problematic paths logged ----------------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## NULL
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 3 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-08-11 21:28:23
## 2 package:for~ <NA>                                 base::l~ 2020-08-11 21:28:23
## 3 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-08-11 21:28:23
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

Much of the functionality in \pkg{fertile} is achieved by writing \href{https://en.wikipedia.org/wiki/Shim_(computing)}{shims}. \pkg{fertile}'s shimmed functions intercept the user's commands and perform various logging and checking tasks before executing the desired function. Our process is:

\begin{enumerate}[noitemsep]
\item Identify an \R function that is likely to be involved in operations that may break reproducibility. Popular functions associated with only one package (e.g., \func{read\_csv} from \pkg{readr}) are ideal candidates.
\item Create a function in \pkg{fertile} with the same name that takes the same arguments (and always the dots \cmd{...}).
\item Write this new function so that it: a) captures any arguments, b) logs the name of the function called, c) performs any checks on these arguments, and d) calls the original function with the original arguments. Except where warranted, the execution looks the same to the user as if they were calling the original function.
\end{enumerate}
Most shims are quite simple and look something like what is shown below for \func{read\_csv}.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function (file, ...) 
## {
##     if (interactive_log_on()) {
##         log_push(file, "readr::read_csv")
##         check_path_safe(file)
##         readr::read_csv(file, ...)
##     }
## }
## <bytecode: 0x7f8f8c998438>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpGDaHPo/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpGDaHPo/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpGDaHPo/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/RtmpGDaHPo/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

The \func{proj\_pkg\_script} function assists with this issue by making it simple and fast to download dependencies. When run on an \R project directory, the function creates a \cmd{.R} script file that contains the code needed to install all of the packages referenced in the project, differentiating between packages located on CRAN and those located on GitHub.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{install_script} \hlkwb{<-} \hlkwd{proj_pkg_script}\hlstd{(proj_dir)}
\hlkwd{cat}\hlstd{(}\hlkwd{readChar}\hlstd{(install_script,} \hlnum{1e5}\hlstd{))}
\end{alltt}
\begin{verbatim}
## # Run this script to install the required packages for this R project.
## # Packages hosted on CRAN...
## install.packages(c( 'broom', 'dplyr', 'ggplot2', 'purrr', 'readr', 'rmarkdown', 'skimr', 'stargazer', 'tidyr' ))
## # Packages hosted on GitHub...
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

However, while the necessity of reproducibility is clear, there are significant behavioral and technical challenges that impede its widespread implementation and no clear consensus on standards of what constitutes reproducibility in published research \citep{peng2009bio}. Not only are the components of reproducible research up for discussion (e.g., need the software be open source?), but the corresponding recommendations for ensuring reproducibility also vary (e.g., should raw and processed data files be in separate directories?).
Existing attempts to address reproducibility in data science are often either too generalized---resulting in shallow and vague recommendations that are challenging to implement---or too specific---approaching one aspect of reproducibility well but doing so in a highly technical way that fails to capture the bigger picture and creates challenges for inexperienced users.

In order to address these challenges, we present \pkg{fertile}\citep{R-fertile}, a low barrier-to-entry package focusing on common reproducibility mistakes programmers make while conducting data science research in R \citep{r-software}.

@@

The \func{proj\_check} function runs sixteen different reproducibility tests, noting which ones passed, which ones failed, the reason for failure, a recommended solution, and a guide to where to look for help. These tests include: looking for a clear build chain, checking to make sure the root level of the project is clear of clutter, confirming that there are no files present that are not being directly used by or created by the code, and looking for uses of randomness that do not have a call to \func{set.seed} present. A full list is provided below:

\vspace{2mm}

\includegraphics[width=500pt,height=280pt]{list-checks}

Subsets of the sixteen tests can be invoked using the \pkg{tidyselect} helper functions \citep{R-tidyselect} in combination with the more limited \func{proj\_check\_some} function. These helper functions, which include \func{starts\_with}, \func{ends\_with}, \func{contains}, and \func{matches}, allow users to check for matches between a string or regular expression and a list of variables--in this case, searching for checks from the list in \func{list\_checks} whose names match a certain condition (i.e. ending with "root").

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Compiling... --------------------------------------------------------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Rendering R scripts... ----------------------------------------------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Running reproducibility checks --------------------------------------------------------- fertile 0.0.0.9027 --}}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Summary of fertile checks -------------------------------------------------------------- fertile 0.0.0.9027 --}}\end{kframe}
\begin{kframe}

@@

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# -- Analysis of reproducibility for project\_miceps ----------------------------------------- fertile 0.0.0.9027 --}}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Packages referenced in source code --------------------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## # A tibble: 9 x 3
##   package       N used_in                    
##   <chr>     <int> <chr>                      
## 1 broom         1 project_miceps/analysis.Rmd
## 2 dplyr         1 project_miceps/analysis.Rmd
## 3 ggplot2       1 project_miceps/analysis.Rmd
## 4 purrr         1 project_miceps/analysis.Rmd
## 5 readr         1 project_miceps/analysis.Rmd
## 6 rmarkdown     1 project_miceps/analysis.Rmd
## 7 skimr         1 project_miceps/analysis.Rmd
## 8 stargazer     1 project_miceps/analysis.Rmd
## 9 tidyr         1 project_miceps/analysis.Rmd
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Files present in directory ----------------------------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## # A tibble: 9 x 4
##   file               ext        size mime                                       
##   <fs::path>         <chr> <fs::byt> <chr>                                      
## 1 Estrogen_Receptor~ docx     10.97K application/vnd.openxmlformats-officedocum~
## 2 citrate_v_time.png png     184.04K image/png                                  
## 3 proteins_v_time.p~ png     377.02K image/png                                  
## 4 Blot_data_updated~ csv      14.43K text/csv                                   
## 5 CS_data_redone.csv csv       7.39K text/csv                                   
## 6 mice.csv           csv      14.33K text/csv                                   
## 7 README.md          md           39 text/markdown                              
## 8 miceps.Rproj       Rproj       204 text/rstudio                               
## 9 analysis.Rmd       Rmd       4.94K text/x-markdown
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Suggestions for moving files --------------------------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## # A tibble: 7 x 3
##   path_rel           dir_rel    cmd                                             
##   <fs::path>         <fs::path> <chr>                                           
## 1 Blot_data_updated~ data-raw   file_move('project_miceps/Blot_data_updated.csv~
## 2 CS_data_redone.csv data-raw   file_move('project_miceps/CS_data_redone.csv', ~
## 3 Estrogen_Receptor~ inst/other file_move('project_miceps/Estrogen_Receptors.do~
## 4 analysis.Rmd       vignettes  file_move('project_miceps/analysis.Rmd', fs::di~
## 5 citrate_v_time.png inst/image file_move('project_miceps/citrate_v_time.png', ~
## 6 mice.csv           data-raw   file_move('project_miceps/mice.csv', fs::dir_cr~
## 7 proteins_v_time.p~ inst/image file_move('project_miceps/proteins_v_time.png',~
\end{verbatim}

{\ttfamily\noindent\itshape\color{messagecolor}{\#\# --\ \  Problematic paths logged ------------------------------------------------------------- fertile 0.0.0.9027 --}}\begin{verbatim}
## NULL
\end{verbatim}
\end{kframe}
\end{knitrout}

\textbf{Both the proactive and retroactive features available in \pkg{fertile} are enabled automatically upon the loading of the package. To prevent users from accidentally enabling or disabling features, \pkg{fertile} does not provide any option to control which features are active. However, those looking to only use the proactive features can do so by refraining from using the retroactive-specific functions while those looking to only use the retroactive features can wait to load \pkg{fertile} until they are ready to produce a report on their project.}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlkwd{log_report}\hlstd{()}
\end{alltt}
\begin{verbatim}
## # A tibble: 3 x 4
##   path         path_abs                             func     timestamp          
##   <chr>        <chr>                                <chr>    <dttm>             
## 1 package:pur~ <NA>                                 base::l~ 2020-10-06 21:01:26
## 2 package:for~ <NA>                                 base::l~ 2020-10-06 21:01:26
## 3 project_mic~ /Users/audreybertin/Documents/ferti~ readr::~ 2020-10-06 21:01:26
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

Much of the functionality in \pkg{fertile} is achieved by writing \href{https://en.wikipedia.org/wiki/Shim_(computing)}{shims}. \textbf{In computer programming generally, a shim is a function that intercepts a user's call, changes the arguments passed to it, and/or modifies the execution of the function in some way.} In the case of \pkg{fertile} specifically, shims are used to intercept the user's commands and perform various logging and path-checking tasks before executing the desired function. Our process is:

\begin{enumerate}[noitemsep]
\item Identify an \R function that is likely to be involved in operations that may break reproducibility. Popular functions associated with only one package (e.g., \func{read\_csv} from \pkg{readr}) are ideal candidates.
\item Create a function in \pkg{fertile} with the same name that takes the same arguments \st{(and always the dots ...)}.
\item Write this new function so that it: a) captures any arguments, b) logs the name of the function called, c) performs any checks on these arguments, and d) calls the original function with the original arguments. Except where warranted, the execution looks the same to the user as if they were calling the original function. Since \pkg{fertile} only needs access to the file path argument, "file" is the only declared argument for most shims. The other arguments are managed using the dots (...), which capture and save them, allowing them to eventually be passed back to the original shimmed function (i.e. \func{readr::read\_csv}).

\end{enumerate}
Most shims are quite simple and look something like what is shown below for \func{read\_csv}.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{fertile}\hlopt{::}\hlstd{read_csv}
\end{alltt}
\begin{verbatim}
## function(file, ...) {
##   if (interactive_log_on()) {
##     log_push(file, "readr::read_csv")
##     check_path_safe(file)
##     readr::read_csv(file, ...)
##   }
## }
## <bytecode: 0x7fbd9847b260>
## <environment: namespace:fertile>
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{proj_dir}
\end{alltt}
\begin{verbatim}
## [1] "project_miceps"
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(proj_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## project_miceps/Blot_data_updated.csv   project_miceps/CS_data_redone.csv      
## project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\begin{alltt}
\hlstd{temp_dir} \hlkwb{<-} \hlkwd{sandbox}\hlstd{(proj_dir)}
\hlstd{temp_dir}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmp54U9ou/project_miceps
\end{verbatim}
\begin{alltt}
\hlstd{fs}\hlopt{::}\hlkwd{dir_ls}\hlstd{(temp_dir)} \hlopt{%>%} \hlkwd{head}\hlstd{(}\hlnum{3}\hlstd{)}
\end{alltt}
\begin{verbatim}
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmp54U9ou/project_miceps/Blot_data_updated.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmp54U9ou/project_miceps/CS_data_redone.csv
## /var/folders/v6/f62qz88s0sd5n3yqw9d8sb300000gn/T/Rtmp54U9ou/project_miceps/Estrogen_Receptors.docx
\end{verbatim}
\end{kframe}
\end{knitrout}

@@

The \func{proj\_pkg\_script} function assists with this issue by making it simple and fast to download dependencies. When run on an \R project directory, the function creates a \cmd{.R} script file that contains the code needed to install all of the packages referenced in the project, differentiating between packages located on CRAN and those located on GitHub.
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlstd{install_script} \hlkwb{<-} \hlkwd{proj_pkg_script}\hlstd{(proj_dir)}
\end{alltt}
\end{kframe}
\end{knitrout}

The package installation script for project miceps looks as follows:

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{verbatim}
## # Run this script to install the required packages for this R project.
## # Packages hosted on CRAN...
## install.packages(c( 'broom', 'dplyr', 'ggplot2', 'purrr', 'readr', 'rmarkdown', 'skimr', 'stargazer', 'tidyr' ))
## # Packages hosted on GitHub...
\end{verbatim}
\end{kframe}
\end{knitrout}

\textbf{\pkg{fertile} also keeps track of dependencies in additional detail. Every time the code contained within a project is rendered by `fertile`, the package generates a file capturing the `sessionInfo()` just after the code was run. This file contains information about the R version in which the code was run, the list of packages that were loaded, and their specific versions.}

\textbf{Users can access this file via the \func{proj\_dependency\_report} function. Its output appears as a new window in RStudio with contents that look like the text below:}

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
\begin{alltt}
\hlcom{##  The R project located at '/Users/audreybertin/Documents/fertile-paper2/STAT-paper-template}
\hlcom{##  /APA/project_miceps' was last run in the following software environment:}

\hlcom{##  R version 4.0.2 (2020-06-22)}
\hlcom{##  Platform: x86_64-apple-darwin17.0 (64-bit)}
\hlcom{##  Running under: macOS Catalina 10.15.5}

\hlcom{##  Matrix products: default}
\hlcom{##  BLAS:   /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRblas.dylib}
\hlcom{##  LAPACK: /Library/Frameworks/R.framework/Versions/4.0/Resources/lib/libRlapack.dylib}

\hlcom{##  locale:}
\hlcom{##  en_US.UTF-8/en_US.UTF-8/en_US.UTF-8/C/en_US.UTF-8/en_US.UTF-8}

\hlcom{##  attached base packages:}
\hlcom{##  stats     graphics  grDevices utils     datasets  methods   base     }

\hlcom{##  other attached packages:}
\hlcom{##  stargazer_5.2.2    skimr_2.1.2        purrr_0.3.4       }
\hlcom{##  ggplot2_3.3.2      tidyr_1.1.2        readr_1.3.1        dplyr_1.0.2}
\end{alltt}
\end{kframe}
\end{knitrout}
